Tor's Usability for Censorship Circumvention

### 2016-04-05 pets2017-paper/pets2017-paper.tex
outlined redesign section

{\color {red} 
Talk about the problems from the previous results section, and how we plan to change them,
along with a heuristic evaluation of the interface.

Talk about the process of designing a new interface, and how we tested it with BLUES and the
Tor Developers.

Talk about the improvements in heuristics from the existing to the redesigned interface, along 
with hopes of what we want our empirical goals to be (to increase success rate and to minimize
time to completion, which we do by some proxy detection, giving specific directions, etc.).

...

Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.\\

%\noindent {\bfseries Design choices}
%The launcher interface utilizes a number of techniques to aid users and simplify
%the choices they have to make. Help buttons and a support email address that
%appears on every screen are meant to assist users that get stuck in the process.
%The interface also makes good use of defaults, for example by emphasizing that
%certain options ``will work in most situations.''
%
%Still, there remains potential for confusion, especially with the more advanced
%configuration options.
%Bridges, pluggable transports, and proxies are never defined for the user,
%arguably because they might not read or understand these definitions.
%This can lead to users confusing these terms, or not understanding
%the relations between them. Additionally, there is limited explanation of 
%what pluggable transport types to choose from if the default one fails or how to 
%find proxy settings, which will be required of some users.

What to talk about in this section: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item Talk about the process of translating observations and feedback into feature changes. 
\item Polishing the interface by working with a designer, using heuristics, and using technical information. 
\item Iterative design and feedback cycle. 
\item How we made a functional, instrumented prototype (forking from the interface repo on github and hacking on it) and instrumented the old prototype. 
\end{itemize}

Talk about how the design as a conservative design. And why the conservative choices were made. For at-risk users, maintainability, etc.
}

>>>>

%skip talking about the process of redesigning the interface. It isn't that interesting.

Changes made: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item Made first screen more clear to help users decide on connect vs configure. 
\item Got rid of question screens. 
\item Put the proxy first. It makes sense topologically. 
\item Added auto-detect for proxies. 
\item Gave explicit advice on how to choose bridges. 
\item Added a summary screen. 
\item Added a topological progress bar that works every time. 
\item Gives instructions on what to try next after failure. 
\item Greatly reduced text and made text easier to read. 
\item Less visual clutter for users. Hide things until user clicks on them. 
\end{itemize}

Talk about how the design as a conservative design. And why the conservative choices were made. For at-risk users, maintainability, etc.
